### 2024-11-22 NN/plots_latex.tex
commit

@@

@@

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Sig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{Sig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Sig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{Sig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Sig1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{Sig1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/SigReLU2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{SigReLU2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/SigReLU2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{SigReLU2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReLUSig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{ReLUSig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReLUSig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{ReLUSig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

### 2024-11-22 NN/plots_preds_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-91.77-Tanh2HiddenLayer-rate.png}
    \caption{Prediction of rate with Tanh2HiddenLayer epochs:50 - R-Squared: 0.92}
\end{figure}
